\plaintitle

### 2017-05-15 papers/IoT2017/paper.tex
formatting fixes

% Paper metadata (use plain text, for PDF inclusion and later
% re-using, if desired).  Use \emtpyauthor when submitting for review
% so you remain anonymous.
\def\plaintitle{Private Blockchains for Transactive Energy}
\def\plainauthor{First Author, Second Author, Third Author}
\def\emptyauthor{}
\def\plainkeywords{Transactive microgrid; blockchain; privacy; security.}
\def\plaingeneralterms{} % TODO!

@@

% TODO!
\category{H.5.m.}{Information Interfaces and Presentation
  (e.g. HCI)}{Miscellaneous} \category{See
  \url{http://acm.org/about/class/1998/} for the full list of ACM
  classifiers. This section is required.}{}{}

@@

\begin{figure}[h!]
\begin{tikzpicture}[
  x=1.04cm,
  nodeStyle/.style={rounded corners=0.1cm, drop shadow={shadow xshift=0.04cm, shadow yshift=-0.05cm, fill=black}}]

@@

\begin{figure}[h!]
\begin{tikzpicture}[
  x=1.6cm,
  font=\small,
  nodeStyle/.style={fill=white, draw=black, drop shadow=black!30, minimum size=0.5cm},
  arrowStyle/.style={->, >=stealth, shorten >=1.5pt, shorten <=1.5pt},
  transactionStyle/.style={draw, align=center, fill=black!10, font=\footnotesize}]
\draw [->, >=stealth] (0.6, 0) -- (5.4, 0) node [right] {time};

@@

\begin{table*}
\caption{Logical Node Types}
\label{tab:logicalNodeTypes}
\begin{tabular}{|c||l|l|l|}
\hline
\textbf{Type} & \textbf{Function} & \textbf{Cardinality} & \textbf{Physical node} \\
\hline\hline
\rowcolor{Gray} Ledger      & maintain distributed ledger                 & one or more           & any node (with enough computational power) \\ \hline
                Trading     & provide trading platform                    & one or more           & any node (with enough computational power) \\ \hline
\rowcolor{Gray} Prosumer    & trade electricity (on behalf of a prosumer) & one for each prosumer & smart inverter or smart meter \\ \hline
                Smart meter & record power consumption and production     & one for each prosumer & smart meter (must be trusted hardware) \\ \hline
\rowcolor{Gray} DSO         & regulate microgrid electricity market       & one                   & node owned by the DSO \\ \hline
\end{tabular}
\end{table*}

@@

\begin{table*}
\caption{Transaction Types}
\label{tab:transactionTypes}
\begin{tabular}{|c||l|l|p{5.8cm}|}
\hline
\textbf{Type} & \textbf{Creator} & \textbf{Contents} & \textbf{Validity} \\
\hline\hline
\rowcolor{Gray} Financial  & prosumers    & identifiers, signatures, time interval, amount of energy & signed by buyer and seller, abides by the safety and security rules \\ \hline
                Energy     & smart meters & identifier, signature, time interval, amount of energy   & signed by smart meter \\ \hline
\rowcolor{Gray} Regulatory & DSO          & signature, time interval, set of policy updates            & signed by DSO \\ \hline
\end{tabular}
\end{table*}

>>>>

% Paper metadata (use plain text, for PDF inclusion and later
% re-using, if desired).  Use \emtpyauthor when submitting for review
% so you remain anonymous.
\def\plaintitle{Private Blockchains for Transactive Energy:\\Security, Privacy, and Safety}
\def\plainauthor{First Author, Second Author, Third Author}
\def\emptyauthor{}
\def\plainkeywords{Internet of Things; blockchain; transactive energy; privacy; security; transactive microgrid.}
\def\plaingeneralterms{Design, Human Factors, Reliability, Security} % TODO: revise

@@

% TODO!
\category{K.6.m}{Miscellaneous}{Security}
\category{D.4.7}{Organization and Design}{Distributed systems}

@@

\begin{figure}[h!]
\center
\begin{tikzpicture}[
  x=1.04cm,
  nodeStyle/.style={rounded corners=0.1cm, drop shadow={shadow xshift=0.04cm, shadow yshift=-0.05cm, fill=black}}]

@@

\begin{figure}[h!]
\center
\begin{tikzpicture}[
  x=1.6cm,
  font=\small,
  nodeStyle/.style={fill=white, draw=black, drop shadow=black!30, minimum size=0.5cm},
  arrowStyle/.style={->, >=stealth, shorten >=1.5pt, shorten <=1.5pt},
  transactionStyle/.style={draw, align=center, fill=black!10, font=\footnotesize}]
\draw [->, >=stealth] (0.6, 0) -- (5.4, 0) node [right] {time};

@@

\begin{table*}
\center
\caption{Logical Node Types}
\label{tab:logicalNodeTypes}
\begin{tabular}{|c||p{4.6cm}|l|l|}
\hline
\textbf{Type} & \textbf{Function} & \textbf{Cardinality} & \textbf{Physical node} \\
\hline\hline
\rowcolor{Gray} Ledger      & maintain distributed ledger                 & one or more           & any node (with enough computational power) \\ \hline
                Trading     & provide trading platform                    & one or more           & any node (with enough computational power) \\ \hline
\rowcolor{Gray} Prosumer    & trade electricity (on behalf of a prosumer) & one for each prosumer & smart inverter or smart meter \\ \hline
                Smart meter & record power consumption and production     & one for each prosumer & smart meter (must be trusted hardware) \\ \hline
\rowcolor{Gray} DSO         & regulate microgrid electricity market       & one                   & node owned by the DSO \\ \hline
\end{tabular}
\end{table*}

@@

\begin{table*}
\center
\caption{Transaction Types}
\label{tab:transactionTypes}
\begin{tabular}{|c||l|l|p{5cm}|}
\hline
\textbf{Type} & \textbf{Creator} & \textbf{Contents} & \textbf{Validity} \\
\hline\hline
\rowcolor{Gray} Financial  & prosumers    & identifiers, signatures, time interval, amount of energy & signed by buyer and seller, abides by the safety and security rules \\ \hline
                Energy     & smart meters & identifier, signature, time interval, amount of energy   & signed by smart meter \\ \hline
\rowcolor{Gray} Regulatory & DSO          & signature, time interval, set of policy updates            & signed by DSO \\ \hline
\end{tabular}
\end{table*}
